\section{Project Aims, Objectives and Abstract}
PAWSTrack is a web-based shelter pet and record management system developed for the local shelter "PAWS" that is run by our own RA, Ahmed Bilal. Currently, the shelter does not have any proper management system, running and working purely on the efforts of some individuals who are managing the shelter. The shelter is in need of a system that can help them manage their pet records, inventory, staff, and vet records, and their finances / donations. The general public also has no formal way of contacting the shelter, or understanding their operations apart from their social media pages, which are also not comprehensive or efficient in providing information to the public.

PAWSTrack aims to streamline shelter operations for the shelter admin by providing efficient record keeping, enhancing workflow, and ensuring data security. The system will allow the admin to manage pet records including their adoption status, medical history and records, shelter inventory and stock, staff and vet's working at the shelter. The general public can also register on the web-page to understand more about the shelter operations, view current pets at the shelter either undergoing some medical treatment or if they are up for adoption. The users can also register their pets for treatments, or donate to the shelter out of good will. The app aims to create awareness amongst the general public while providing them with a platform to interact with the shelter. 

Key features include a user-friendly interface, scalability, and robust privacy measures. PAWSTrack serves as an intuitive solution for managing pet records, veterinary services, and inventory, contributing to the overall well-being of the shelter and its furry residents.